---
output: 
  pdf_document: 
    fig_caption: no
header-includes:
  - \usepackage{pdfpages}
urlcolor: blue
editor_options: 
  chunk_output_type: console
---

\fontsize{11}{22}
\renewcommand{\familydefault}{\sfdefault}

# State Supplementary Results
## COVID-19 Scenario Modeling Hub Report: Round 19 - 2025 to 2026 Season
`r format(Sys.time(), '%d %B, %Y')`\
Scenario Modeling Hub Team^[Compiled by Shaun Truelove, Sung-mok Jung, Lucie Contamin, Cécile Viboud, and Justin Lessler.]


This supplementary report contains state-level results for each state. These results mirror those at the national level. See [covid19scenariomodelinghub.org](https://covid19scenariomodelinghub.org/) and the main report for more details.


```{r setup, include=FALSE}


rerun_metaanalysis <- TRUE

### path to local version of repository
#local_path <- "/Users/eah394/Documents/GitHub/"
#local_path <- "C:/Users/clair/Documents/COVID/SMH/"
# local_path <- "/Users/saraloo/Documents/SMH/COVID/"
# local_path <- "C:/Users/ecarcele/Documents/JHUProjects/SMH/COVID/"


local_path <- file.path(dirname(here::here()))
this_path <- here::here()

dir_path <- file.path(local_path, "covid19-scenario-hub_analysis")
data_path <- file.path(local_path, "covid-19-smh_data")
smh_path <- file.path(local_path, "covid19-scenario-modeling-hub")
web_path <- file.path(local_path, "covid19-scenario-hub_website")

# sys_call <- paste0("cd ", dir_path, "/ && git pull && timeout /t 30 /nobreak && ", 
#               "cd ", data_path, "/ && git pull && timeout /t 30 /nobreak && ", 
#               "cd ", web_path, "/ && git pull && timeout /t 30 /nobreak && ", 
#               "cd ", this_path, "/")
# system(sys_call)


knitr::opts_chunk$set(echo = FALSE, warning = FALSE,
                      cache.lazy = FALSE,
                      dev = 'pdf', 
                      message=FALSE, cache=FALSE,
                      include = FALSE)

knitr::opts_knit$set(root.dir = dir_path)

library(tidyverse)
library(readr)
library(scales)
library(purrr)
library(ggpmisc)
library(usmap)
library(reshape2)
library(data.table)
library(arrow)
library(tidytext)
library(lubridate)
library(jsonlite)
library(hubUtils)


```

```{r report_prep, message=FALSE, warning=FALSE, cache=FALSE, include=FALSE}
# add to options to cache data build ---  

# Get Round Metadata
round_metadata <- hubUtils::read_config(smh_path, "tasks")
round_id <- max(get_round_ids(round_metadata))
folder_path <- file.path("model-processed", round_id)


## choose scenario identifier and appropriate hosp file
scenario.id <- "2025-04-01"
projection.start.date <- round_id
projection.end.date <- "2026-04-25"
year_start <- 2025
year_end <- 2026
round <- 19
ens_choice <- "Ensemble_LOP"
pi_low <- 0.025
pi_high <- 0.975  


# load metadata on Round

model_names <- list.dirs(file.path(data_path, "model-processed", round_id), 
                         full.names = FALSE, 
                         recursive = FALSE) 

model_names <- c(model_names[grepl("Ensemble", model_names)], 
                 model_names[!grepl("Ensemble", model_names)]) # put ensemble first


# load(paste0(web_path,"visualization/data-visualization/sysdata.rda"))

# Scenario name information - UPDATE EACH ROUND
axis1 <- c("noBoo", "HighRiskVax", "allVax")
axis2 <- c("noTiming", "classicTiming", "earlyTiming")
axis1_long <- c("No booster", "65+ and high-risk booster", "All booster")
axis2_long <- c("No Immunization", "Classic Immunization", "Early Immunization") 
var_name1 <- "booster"
var_name2 <- "timing"
pessimistic <- paste0(axis1[1], "_", axis2[1]) # most pessimistic scenario to use for risk maps

scn_combos <- list(
  c(1,1),
  c(2,2),
  c(2,3),
  c(3,2),
  c(3,3)
)

# set the axis and scenario names and labels
scn_names <- sapply(scn_combos, function(x) paste(axis1[x[1]], axis2[x[2]], sep = "_"))
scenario_ids <- paste0(LETTERS[1:length(scn_names)], "-", scenario.id)
a1 <- sapply(scn_combos, function(x) axis1[x[1]])
a2 <- sapply(scn_combos, function(x) axis2[x[2]])
a1long <- sapply(scn_combos, function(x) axis1_long[x[1]])
a2long <- sapply(scn_combos, function(x) axis2_long[x[2]])



# Locations

# test data
config_json <- hubUtils::read_config(smh_path, "tasks")
schema <- hubData::create_hub_schema(config_json)

# Prerequisite ======
df_loc <- read.csv(file.path(smh_path, "auxiliary-data/data-locations/locations_2022.csv")) %>%
  dplyr::select(-age_group, - population) %>% distinct()

# Load data =====
dc <- arrow::open_dataset(file.path(data_path, folder_path),
                          partitioning = c("model_id", "target", "location"),
                          hive_style = FALSE, schema = schema,
                          factory_options = list(exclude_invalid_files = TRUE))
locs_df <- dplyr::filter(dc, model_id == "Ensemble_LOP", 
                         output_type == "quantile", output_type_id == 0.5,
                         scenario_id == "B-2025-04-01",
                         # scenario_id %in% c("A-2025-04-01", "B-2025-04-01"), 
                         age_group == "0-130",
                         target == "inc hosp") |> 
  dplyr::collect() %>% dplyr::select(location) |> distinct()

locs_df <- dplyr::left_join(locs_df, df_loc, by = c("location")) |>
  dplyr::mutate(loc_numeric = as.integer(location)) %>%
  dplyr::mutate(loc_numeric = ifelse(location == "US", 0, loc_numeric)) %>%
  arrange(loc_numeric) %>%
  dplyr::mutate(location = factor(location, levels = location)) %>%
  arrange(location)

```

## Round 19 Scenario Specifications
![Round 19 Scenario Specifications](`r file.path(smh_path,"auxiliary-data/rounds", paste0("round", round, "_viz"), paste0("covid19_round", round, ".png"))`)



```{r run_states, include=FALSE, echo=FALSE, cache=FALSE, results='asis', eval = TRUE}

# Loop through the three locations and knit child documents
locs <- as.character(unique((locs_df %>% filter(location!="US"))$location))
# locs <- c("01", "02", "04")
# locs <- c("01")
res <- vector(mode = "list", length = length(locs))


panel_height <- 5.5

unmatched_models <- NA
numdiff_for_text <- NULL
reldiff_for_text <- NULL

# for (i in locs) {
  
  # loc_select <- i
  # loc_name <- locs_df$location_name[locs_df$location == loc_select]
  # loc_abbr <- locs_df$abbreviation[locs_df$location == loc_select]
  # 
  # # print(getwd())
  # 
  # loc_subname <- ifelse(loc_select == "US", "", paste0("_", loc_abbr))
  # 
  # # load data from the round for trajectories
  # # source(file.path(dir_path,"code/R/read_sample_files.R"), local = knitr::knit_global())
  # source(file.path(dir_path,"code/R/read_sample_files_locs.R"), local = FALSE)
  # 
  # # Run each meta analysis
  # 
  # # overall
  # panel_height <- 7.5
  # age_group_tmp <- "0-130"
  # age_group_label <- "Overall"
  # source(file.path(dir_path,"code/R/sample_based_effect_estimates_overall.R"), local = FALSE)
  # source(file.path(dir_path,"code/R/sample_based_effect_estimates_timing.R"), local = knitr::knit_global())
  # # 0-64
  # panel_height <- 7
  # age_group_tmp <- "0-64"
  # age_group_label <- "0-64"
  # source(file.path(dir_path,"code/R/sample_based_effect_estimates_overall.R"), local = knitr::knit_global())
  # source(file.path(dir_path,"code/R/sample_based_effect_estimates_timing.R"), local = knitr::knit_global())
  # # 65+
  # panel_height <- 7
  # age_group_tmp <- "65-130"
  # age_group_label <- "65+"
  # source(file.path(dir_path,"code/R/sample_based_effect_estimates_overall.R"), local = knitr::knit_global())
  # source(file.path(dir_path,"code/R/sample_based_effect_estimates_timing.R"), local = knitr::knit_global())
  # 
  # gc()
  # rm(df_sample)
  # gc()
  # 
  # # set the location in the environment
  # assign("loc_select", loc_select, envir = environment())
  # assign("loc_name", loc_name, envir = environment())
  # assign("loc_abbr", loc_abbr, envir = environment())
  
  # # knit the child document
  # res[[i]] <- knitr::knit_child("reports/report_generator_r19_StateSupplement_test.Rmd", quiet = TRUE, envir = environment())
  
# }
# cat(unlist(res), sep = '\n')

```


```{r, include=FALSE, echo=FALSE, cache=FALSE, results='asis', eval=TRUE}

out2 <- lapply(
  unique(locs),
  FUN = function(x) {
    
    loc_select <- x
    loc_name <- locs_df$location_name[locs_df$location == loc_select]
    loc_abbr <- locs_df$abbreviation[locs_df$location == loc_select]
    
    # set the location in the environment
    assign("loc_select", loc_select, envir = environment())
    assign("loc_name", loc_name, envir = environment())
    assign("loc_abbr", loc_abbr, envir = environment())
    
    knitr::knit_expand(
      file = "reports/report_generator_r19_StateSupplement_source.Rmd",
      loc_select = loc_select
    )
  }
)
```


```{r, include=TRUE, echo=FALSE, cache=FALSE, results='asis', eval=TRUE}

res <- knitr::knit_child(text = unlist(out2), quiet = TRUE)
cat(res, sep = '\n')

```



\newpage

# Teams and Models
- Center for Forecasting and Outbreak Analytics (CFA) - CFA-Scenarios
  * Laura Albrecht, Elisha Are, Michael Batista, Ariel Shurygin, Kok Ben Toh, Thomas Hladish
- Johns Hopkins and UNC ID Dynamics  — JHU_UNC-flepiMoP
  * Anjalika Nande (JHU IDD), Sara Loo (Johns Hopkins Infectious Disease Dynamics [JHU IDD]), Joseph C. Lemaitre (University of North Carolina at Chapel Hill [UNC]), Timothy Willard (UNC), Carl Pearson (UNC), Allison Hill (JHU IDD), Justin Lessler (JHU IDD, UNC), Shaun Truelove (JHU IDD)
- Northeastern University MOBS Lab — MOBS_NEU-GLEAM_COVID
  * Matteo Chinazzi (Laboratory for the Modeling of Biological and Socio-technical Systems, Northeastern University, Boston, MA [NEU]), Jessica T. Davis (NEU), Alessandro Vespignani (NEU)
- University of Illinois at Urbana-Champaign - UIUC-IMMCYC
  * Soren L Larsen (UIUC)
- University of North Carolina at Charlotte - UNCC-Hierbin
  * Shi Chen (UNCC Dept. of Public Health Sciences & School of Data Science), Rajib Paul (UNCC Dept. of Public Health Sciences and School of Data Science), Daniel Janies (UNCC Dept. of Bioinformatics and Genomics)
- University of Texas at Austin - ImmunoSEIRS
  * Shraddha Ramdas Bandekar (UTA), Anass Bouchnita (UT-El Paso), Spencer Fox (University of Georgia), Michael Lachmann (UTA), Lauren Ancel Meyers (UTA)
- University of Virginia — Adaptive
  * Przemyslaw Porebski (UVA), Srini Venkatramanan (UVA), Bryan Lewis (UVA), Aniruddha Adiga (UVA), Jiangzhuo Chen (UVA), Anil Vullikanti (UVA), Madhav Marathe (UVA)
- Predictive Science - PSI-M_CoV_2025
  * Jamie Turtle, Michal Ben-Nun, Pete Riley

## The COVID-19 Scenario Modeling Hub Team
- Justin Lessler, University of North Carolina, Chapel Hill
- Cécile Viboud, NIH Fogarty
- Shaun Truelove, Johns Hopkins University
- Katriona Shea, Penn State University
- Claire Smith, University of North Carolina, Chapel Hill
- Emily Howerton, Penn State University
- Harry Hochheiser, University of Pittsburgh
- Michael Runge, USGS
- Lucie Contamin, University of Pittsburgh
- Sara Loo, Johns Hopkins University
- Sung-mok Jung, University of North Carolina, Chapel Hill
- Erica Carcelén, Johns Hopkins University
- Hidetoshi Inamine, Penn State University


