---
output: 
  pdf_document: 
    fig_caption: no
header-includes:
  - \usepackage{pdfpages}
urlcolor: blue
editor_options: 
  chunk_output_type: console
---

\fontsize{11}{22}
\renewcommand{\familydefault}{\sfdefault}


# Round 19 Executive Summary Report
COVID-19 Scenario Modeling Hub, `r format(Sys.time(), '%d %B, %Y')`\
<!-- Scenario Modeling Hub Team -->
<!-- ^[Compiled by Shaun Truelove, Sung-mok Jung, Lucie Contamin, Cécile Viboud, and Justin Lessler.] -->

```{r setup, include=FALSE}

rerun_metaanalysis <- TRUE
loc_select <- "US"


### path to local version of repository
#local_path <- "/Users/eah394/Documents/GitHub/"
#local_path <- "C:/Users/clair/Documents/COVID/SMH/"
# local_path <- "/Users/saraloo/Documents/SMH/COVID/"
# local_path <- "C:/Users/ecarcele/Documents/JHUProjects/SMH/COVID/"


local_path <- file.path(dirname(here::here()))
this_path <- here::here()

dir_path <- file.path(local_path, "covid19-scenario-hub_analysis")
data_path <- file.path(local_path, "covid-19-smh_data")
smh_path <- file.path(local_path, "covid19-scenario-modeling-hub")
web_path <- file.path(local_path, "covid19-scenario-hub_website")

# sys_call <- paste0("cd ", dir_path, "/ && git pull && timeout /t 30 /nobreak && ", 
#               "cd ", data_path, "/ && git pull && timeout /t 30 /nobreak && ", 
#               "cd ", web_path, "/ && git pull && timeout /t 30 /nobreak && ", 
#               "cd ", this_path, "/")
# system(sys_call)


knitr::opts_chunk$set(echo = FALSE, warning = FALSE,
                      cache.lazy = FALSE,
                      dev = 'pdf')
knitr::opts_knit$set(root.dir = dir_path)

library(tidyverse)
library(readr)
library(scales)
library(purrr)
library(ggpmisc)
library(usmap)
library(reshape2)
library(data.table)
library(arrow)
library(tidytext)
library(lubridate)
library(jsonlite)
library(hubUtils)


```

```{r report_prep, message=FALSE, warning=FALSE, cache=FALSE, include=FALSE}
# add to options to cache data build ---  

# Get Round Metadata
round_metadata <- hubUtils::read_config(smh_path, "tasks")
round_id <- max(get_round_ids(round_metadata))

# get_round_model_tasks(round_metadata, round_id = round_id)
# get_round_model_tasks(round_metadata, round_id = round_id)



## choose scenario identifier and appropriate hosp file
scenario.id <- "2025-04-01"
projection.start.date <- round_id
projection.end.date <- "2026-04-25"
year_start <- 2025
year_end <- 2026
round <- 19
ens_choice <- "Ensemble_LOP"
pi_low <- 0.025
pi_high <- 0.975  



# load metadata on Round

model_names <- list.dirs(file.path(data_path, "model-processed", round_id), 
                         full.names = FALSE, 
                         recursive = FALSE) 

model_names <- c(model_names[grepl("Ensemble", model_names)], 
                 model_names[!grepl("Ensemble", model_names)]) # put ensemble first

# model_names <- c("Ensemble",
#                  "Ensemble_LOP",
#                  "Ensemble_LOP_untrimmed",
#                  "JHU_UNC-flepiMoP",
#                  "MOBS_NEU-GLEAM_COVID",
#                  "NotreDame-FRED",
#                  "PSI-PROF",
#                  "UNCC-hierbin",
#                  "USC-SIkJalpha",
#                  "UTA-ImmunoSEIRS",
#                  "UVA-adaptive",
#                  "CFA-Scenarios")


# load(paste0(web_path,"visualization/data-visualization/sysdata.rda"))

# Scenario name information - UPDATE EACH ROUND
axis1 <- c("noBoo", "HighRiskVax", "allVax")
axis2 <- c("noTiming", "classicTiming", "earlyTiming")
axis1_long <- c("No booster", "65+ and high-risk booster", "All booster")
axis2_long <- c("No Immunization", "Classic Immunization", "Early Immunization") 
var_name1 <- "booster"
var_name2 <- "timing"
pessimistic <- paste0(axis1[1], "_", axis2[1]) # most pessimistic scenario to use for risk maps

scn_combos <- list(
  c(1,1),
  c(2,2),
  c(2,3),
  c(3,2),
  c(3,3)
)



# set the axis and scenario names and labels
scn_names <- sapply(scn_combos, function(x) paste(axis1[x[1]], axis2[x[2]], sep = "_"))
scenario_ids <- paste0(LETTERS[1:length(scn_names)], "-", scenario.id)
a1 <- sapply(scn_combos, function(x) axis1[x[1]])
a2 <- sapply(scn_combos, function(x) axis2[x[2]])
a1long <- sapply(scn_combos, function(x) axis1_long[x[1]])
a2long <- sapply(scn_combos, function(x) axis2_long[x[2]])


```


```{r load_trajdata, include=FALSE, echo = FALSE, warning = FALSE}

if(rerun_metaanalysis){
  
  unmatched_models <- NA
  
  # load data from the round for trajectories
  # source(file.path(dir_path,"code/R/read_sample_files.R"), local = knitr::knit_global())
  source(file.path(dir_path,"code/R/read_sample_files_US.R"), local = knitr::knit_global())
  
  # Run each meta analysis
  
  # overall
  age_group_tmp <- "0-130"
  age_group_label <- "Overall"
  source(file.path(dir_path,"code/R/sample_based_effect_estimates_overall.R"), local = knitr::knit_global())
  source(file.path(dir_path,"code/R/sample_based_effect_estimates_timing.R"), local = knitr::knit_global())
  # 0-64
  age_group_tmp <- "0-64"
  age_group_label <- "0-64"
  source(file.path(dir_path,"code/R/sample_based_effect_estimates_overall.R"), local = knitr::knit_global())
  source(file.path(dir_path,"code/R/sample_based_effect_estimates_timing.R"), local = knitr::knit_global())
  # 65+
  age_group_tmp <- "65-130"
  age_group_label <- "65+"
  source(file.path(dir_path,"code/R/sample_based_effect_estimates_overall.R"), local = knitr::knit_global())
  source(file.path(dir_path,"code/R/sample_based_effect_estimates_timing.R"), local = knitr::knit_global())
  
  gc()
  rm(df_sample)
  gc()
}

```





```{r load_quantdata, include=FALSE}

print(dir_path)
source(file.path(dir_path,"code/R/read_data_files.R"), local = knitr::knit_global())
source(file.path(dir_path,"code/R/collect_data_update.R"), local = knitr::knit_global())
gc()

```



```{r format_data, include = FALSE}

# some columns to use for plotting
names(scn_names) <- scenario_ids
names(a1) <- scenario_ids
names(a2) <- scenario_ids
names(a1long) <- scenario_ids
names(a2long) <- scenario_ids


quant_data_ci <- quant_data_ci %>%
  mutate(model = factor(model, levels = model_names)) %>%
  mutate(scenario_name = recode(scenario_id, !!! scn_names)) %>%
  mutate(a1 = recode(scenario_id, !!! a1)) %>%
  mutate(a2 = recode(scenario_id, !!! a2)) %>%
  mutate(a1long = recode(scenario_id, !!! a1long)) %>%
  mutate(a2long = recode(scenario_id, !!! a2long)) %>%
  mutate(a1long = factor(a1long, levels = axis1_long)) %>%
  mutate(a2long = factor(a2long, levels = axis2_long)) %>%
  mutate(full_scenario = paste(a1long, a2long, sep = ", "))


quant_data <- quant_data %>%
  mutate(model = factor(model, levels = model_names)) %>%
  mutate(scenario_name = recode(scenario_id, !!! scn_names)) %>%
  mutate(a1 = recode(scenario_id, !!! a1)) %>%
  mutate(a2 = recode(scenario_id, !!! a2)) %>%
  mutate(a1long = recode(scenario_id, !!! a1long)) %>%
  mutate(a2long = recode(scenario_id, !!! a2long)) %>%
  mutate(a1long = factor(a1long, levels = axis1_long)) %>%
  mutate(a2long = factor(a2long, levels = axis2_long)) %>%
  mutate(full_scenario = paste(a1long, a2long, sep = ", "))


# filter out projections beyond 26 weeks
quant_data <- quant_data %>% filter(target_end_date <= as.Date(projection.end.date))
quant_data_ci  <- quant_data_ci  %>% filter(target_end_date <= as.Date(projection.end.date))

```


```{r viz_setup, include=FALSE, echo = FALSE, warning = FALSE}
## parameters for visualization



model_size <- c(0.7, rep(.3, length(model_names)-1))
names(model_size) <- model_names

model_colors <- c(rep("#000000", sum(grepl("Ensemble", model_names))), 
                  c("#E69F00", "#009E73", "#332288", "#56B4E9", "#661100", "#F0E442", "#CC79A7", "#D55E00", "#0072B2")[1:sum(!grepl("Ensemble", model_names))])
names(model_colors) <- model_names

# colorblind friendly palette, note: may need to change with more teams
# additional options - "#D55E00", "#0072B2"
# model_colors <- c("Ensemble" = "#000000", 
#                   "JHU_UNC-flepiMoP" = "#E69F00", #"CU-AGE-ST" = "#D55E00",
#                   "MOBS_NEU-GLEAM_COVID" = "#009E73", #"JHUAPL-Bucky" = "0072B2",  
#                   "NotreDame-FRED" = "#332288", 
#                   "PSI-PROF" = "#56B4E9", #"Karlen-pypm" = "#56B4E9", "UF-ABM" = "#56B4E9", 
#                   "UNCC-hierbin" = "#661100", 
#                   "USC-SIkJalpha" = "#F0E442",
#                   "UTA-ImmunoSEIRS" = "#56B4E9",
#                   "UVA-adaptive" = "#CC79A7",
#                   "CFA-Scenarios" = "#D55E00")

# scenarios <- c(s1.1, s1.2, s2.1, s2.2, s3.1, s3.2)

# make scenario labels more explicit
# first set on one line
scenario_labs <- sapply(scn_combos, function(x) paste(axis1_long[x[1]], axis2_long[x[2]], sep = ", "))
names(scenario_labs) <- scn_names
# second set on two lines
scenario_labs_2 <- sapply(scn_combos, function(x) paste(axis1_long[x[1]], axis2_long[x[2]], sep = "\n"))
names(scenario_labs_2) <- scn_names


# other
breaks <- seq(as.Date("2020-01-01"), as.Date(projection.end.date), "4 month") #as.Date("2021-07-01")
targets <- c("Hospitalizations", "Deaths")
agegroups <- c("0-130", "0-64", "65-130")
lev <- unique(loc$location_name) 

v_line = data.frame(x = as.numeric(as.Date(projection.start.date)),
                    y = Inf,
                    lab = paste0("Projections begin\n",projection.start.date),
                    target_type = "Hospitalizations")


# prior season max
prior_max = truth %>%
  filter(date >= paste0((lubridate::year(round_id)-1), "-04-01") & date < as.Date(projection.start.date)) %>%
  group_by(target_type, location, location_name, age_group) %>%
  summarise(max_value = max(value, na.rm = TRUE)) %>%
  ungroup() 

# #define CDC community transmission thresholds
# h_line_medthr = data.frame(x = Inf,
#                            y = 32872.85,
#                            lab = paste0("Medium Threshold: 32873"),
#                            target_type = "Hospitalizations")
# 
# h_line_highthr = data.frame(x = Inf,
#                             y = 65745.69,
#                             lab = paste0("High Threshold: 65746"),
#                             target_type = "Hospitalizations")


terr <- c("60", "66", "69", "74", "78")
```


```{r}
# filter truth data starting Nov 1 year before only to make projections more visible
truth = truth %>% filter(date >= paste0((lubridate::year(round_id)-1), "-11-01"))
```


## General Dynamics

* **Based on the national ensemble, we expect two periods of increased COVID-19 activity, in summer 2025 and winter 2025-26, in each scenario**, with a first peak projected in late August 2025 and a second peak in January 2026, for both hospitalizations and deaths. Based on the 50% projection interval, both peaks are expected to remain close to that of last winter season (i.e., 20,000 weekly hospitalizations nationally). 

* **Among all scenarios, continued substantial burden of disease from COVID-19 is expected**, with 648,000 cumulative hospitalizations (95% PI 241,000–778,000) and 40,000 deaths (95% PI 25,000-59,000) due to COVID-19 projected over the course of the projection period (April 27, 2025 to April 25, 2026) in the high risk group scenario (i.e., booster vaccination only among individuals aged 65+ or otherwise at high risk for elevated severity). 

```{r, fig.width = 10, fig.height=4.7}

truth_toplot <- truth %>%
  filter(age_group == "0-130" | is.na(age_group))
v_line_toplot <- v_line %>% dplyr::select(-target_type)

temp <- quant_data %>%
  filter(model == "Ensemble", age_group == "0-130", 
         output_type == "quantile", str_detect(target, "inc"), abbreviation == "US") %>% 
  filter(is.na(type)) %>%
  pivot_wider(names_from = quantile, names_prefix = "q") %>%
  mutate(a1 = factor(a1, levels = axis1)) %>%
  mutate(a2 = factor(a2, levels = axis2)) %>%
  arrange(a1, a2) %>%
  filter(a2 != "earlyTiming")

plot <- list()

for (i in targets){
  plot[[i]] <- ggplot(data = temp %>% filter(target_type == i)) +
    geom_vline(data = v_line_toplot, aes(xintercept = x), color = "grey60")+
    geom_text(data = v_line_toplot, aes(x = x, y = y, label = lab), hjust = 0, vjust = 1, size = 3)+
    # geom_hline(data = temp_thresholds, aes(yintercept = y), color = "red", linetype = 2, alpha = 0.2) +
    # geom_text(data = temp_thresholds, aes(x = x, y = y, label = lab), color = "red", hjust = 1, vjust = 0.25, size = 3) +
    # geom_hline(data = h_line_highthr, aes(yintercept = y), color = "red", linetype = 2, alpha = 0.2) + 
    geom_ribbon(aes(x = target_end_date, ymin = q0.025, ymax = q0.975), alpha = 0.2) +
    geom_ribbon(aes(x = target_end_date, ymin = q0.05, ymax = q0.95), alpha = 0.2) +
    geom_ribbon(aes(x = target_end_date, ymin = q0.1, ymax = q0.9), alpha = 0.2) +
    geom_ribbon(aes(x = target_end_date, ymin = q0.25, ymax = q0.75), alpha = 0.2) +
    geom_point(data = truth_toplot %>% filter(target_type == i, location == "US"), 
                             size = 1, aes(x = date, y = value)) +
    facet_wrap(~ a1) +
    theme_bw() +
    xlab(NULL) +
    scale_x_continuous(breaks = breaks, expand = c(0,0), labels = format(breaks, "%b-%Y")) +
    ggtitle(paste0("National ensemble projections - ", i)) +
    theme(text = element_text(size=15),
          axis.text.x = element_text(size=12, angle = 45, vjust =1, hjust=1), 
          axis.title = element_blank(),
          legend.position = "none",
          plot.title = element_text(size=16, hjust = 0),
          plot.caption = element_text(hjust = 0.5),
          # strip.background = element_blank(),
          strip.placement = "outside") +
    (if(i == "Deaths") {
      labs(caption = "From lightest to darkest shading represents 95%, 90%, 80% and 50% projection intervals")
    }) +
    (if(i == "Hospitalizations") {
      theme(
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank()
      )
    })
}

cowplot::plot_grid(plotlist = plot, ncol = 1, align = "v", axis = "lr", rel_heights = c(1, 1.5))

```
\

* **The majority of hospitalization and death burden from COVID-19 is expected to occur in individuals 65+**, with 56% of hospitalizations and 84% of deaths occurring in 65+ in the high-risk group recommendation scenario.


```{r, echo = FALSE, warning = FALSE, fig.width = 11, fig.height=3.4}

temp_hosp <- quant_data  %>% 
  filter(scenario_id == "B-2025-04-01") %>%
  filter(str_detect(target, "cum"), location == "US", model == "Ensemble", target_type == "Hospitalizations") %>%
  filter(target_end_date == max(target_end_date)) %>%
 mutate(agegroup = case_when(age_group == "0-130" ~ "Total population", 
                              age_group == "0-64" ~ "Age 0-64", age_group == "65-130" ~ "Aged 65+")) %>%
  dplyr::filter(quantile %in% c(0.025, 0.25, 0.50, 0.75, .975) & is.na(type)) %>%
  mutate(quantile = as.character(quantile*100)) %>%
  pivot_wider(names_from = quantile, names_prefix = "q")

temp_death <- quant_data %>% 
  filter(scenario_id == "B-2025-04-01") %>%
  filter(str_detect(target, "cum"), location == "US", model == "Ensemble", target_type == "Deaths") %>%
  filter(target_end_date == max(target_end_date)) %>%
  mutate(agegroup = case_when(age_group == "0-130" ~ "Total population", 
                              age_group == "0-64" ~ "Age 0-64", age_group == "65-130" ~ "Aged 65+")) %>%
  dplyr::filter(quantile %in% c(0.025, 0.25, 0.50, 0.75, .975) & is.na(type)) %>%
  mutate(quantile = as.character(quantile*100)) %>%
  pivot_wider(names_from = quantile, names_prefix = "q")

temp_hosp <- temp_hosp %>%
  filter(scenario_id != names(scn_names)[1]) %>%
  bind_rows(temp_hosp %>%
              filter(scenario_id == names(scn_names)[1]) %>%
              mutate(a2 = axis2[2],
                     a2long = axis2_long[2])) %>%
  bind_rows(temp_hosp %>%
              filter(scenario_id == names(scn_names)[1]) %>%
              mutate(a2 = axis2[3],
                     a2long = axis2_long[3]))

temp_death <- temp_death %>%
  filter(scenario_id != names(scn_names)[1]) %>%
  bind_rows(temp_death %>%
              filter(scenario_id == names(scn_names)[1]) %>%
              mutate(a2 = axis2[2],
                     a2long = axis2_long[2])) %>%
  bind_rows(temp_death %>%
              filter(scenario_id == names(scn_names)[1]) %>%
              mutate(a2 = axis2[3],
                     a2long = axis2_long[3]))

temp_outcomes <- temp_hosp %>% bind_rows(temp_death)

temp_outcomes %>%
  mutate(target_type = factor(target_type, levels = c("Hospitalizations", "Deaths"))) %>%
  ggplot() +
  geom_boxplot(aes(x = agegroup,color = agegroup, 
                   ymin = q2.5, lower = q25, middle = q50, upper = q75, ymax = q97.5), stat = "identity") +
  ggtitle("Cumulative COVID-19 hospitalizations and deaths projected in the US") +
  labs(x = NULL,
       y = "Cumulative counts", 
       caption = paste0("Median ensemble projections with 50% and 95% projection intervals, ", 
                        format(as.Date(projection.start.date), "%B %d, %Y"), " to ", 
                        format(as.Date(projection.end.date), "%B %d, %Y"), "\nHigh-risk vaccination scenario")) +
  facet_wrap(~target_type, ncol = 2, scales = "free_y") +
  guides(colour = guide_legend(nrow = 1))+
  scale_color_brewer(palette = "Set2")  +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(labels = comma) +
  theme_bw()+
  theme(text = element_text(size=15),
        axis.text.x = element_text(size=10), 
        axis.title = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank(),
        plot.title = element_text(size=18, hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # strip.background = element_blank(),
        strip.placement = "outside",
        panel.spacing = unit(1, "cm", data = NULL))


# temp_outcomes %>%
#   filter(age_group != "0-130") %>%
#   group_by(target) %>%
#   mutate(med_prop = q50 / sum(q50, na.rm = TRUE)) %>%
#   ungroup() %>%
#   dplyr::select(age_group, target, med_prop)

```




\newpage    

## Impact of Vaccination

* **Both vaccination strategies are projected to significantly reduce disease burden compared to no vaccination**. 

* **Compared to no vaccination, vaccination of high-risk groups reduces hospitalizations by 13% (8-17%) and deaths by 16% (11-21%)**, over the full time period. Vaccinating high-risk groups would result in 90,000 (53,000-126,000) fewer hospitalizations and 7,000 (4,000-9,000) fewer deaths nationally over the projection period, compared to no vaccination. 

* **Vaccination for all age groups increases these reductions to 116,000 (69,000-163,000) hospitalizations and 8,000 (5,000-12,000) deaths averted.** As compared to vaccinating only 65+ and high-risk individuals, vaccinating all ages would prevent an extra 26,000 hospitalizations and 1,000 deaths. 

![Overall pooled differences between scenarios among the total population](`r file.path(dir_path, "reports", paste0("round", round), "figures/combined_simple_0_130.png")`)
\

* **The majority of the overall vaccination benefits (i.e., direct and indirect effects) is expected to come from reductions in this age group,** with 67,000 (38,000-96,000) hospitalizations and 6,000 (4,000-7,000) deaths averted among 65+ individuals in the high-risk group recommendation scenario compared to no vaccination.

* **We estimate that indirect effects of universal vaccine recommendations could reduce disease burden by 4% among people 65+**, representing an additional ~12,000 hospitalizations and ~1,000 deaths averted among this age group. 


