---
title: "Vaccine + wave timing analysis"
output: html_notebook
---

## Setup
```{r setup, include=FALSE}

library(arrow)
library(dplyr)
library(ggplot2)
library(patchwork)
library(MMWRweek)
library(ggpmisc)
library(mclust)
library(tidyverse)
library(broom)
library(RColorBrewer)

```

## File paths
```{r}

# Path to the current repo (cloned from https://github.com/midas-network/covid19-scenario-hub_r19_manuscript)
#repo_path <- "~/Dropbox/GitReps/covid19-scenario-hub_r19_manuscript/"  
repo_path <- "~/Documents/GitHub/covid19-scenario-hub_r19_manuscript/"
folder_path <- "data/model-processed/"

#plot_path = "~/Dropbox/CSJT01/smh_covid_r19/manuscript/analysis/plots"
plot_path = "~/Library/CloudStorage/Box-Box/SMH Rounds/Round19ManuscriptPlots/Plots"

```

## Bookkeeping
```{r}
proj_start_date = as.Date("2025-04-27")

scenario_ids = c("A-2025-04-01", "B-2025-04-01", "C-2025-04-01", 
                 "D-2025-04-01", "E-2025-04-01")
scenarios = c("A", "B", "C", "D", "E")

# Establish schema
schema <- arrow::schema(
  arrow::field("origin_date", arrow::string()),
  arrow::field("scenario_id", arrow::string()),
  arrow::field("location", arrow::string()),
  arrow::field("target", arrow::string()),
  arrow::field("horizon", arrow::int64()),
  arrow::field("output_type", arrow::string()),
  arrow::field("output_type_id", arrow::int64()),
  arrow::field("age_group", arrow::string()),
  arrow::field("model_id", arrow::string()),
  arrow::field("value", arrow::float64()),
)

# declare models that will be up-sampled
upsamp_mods = c("UNCC-Hierbin", "UT-ImmunoSEIRS", "UVA-adaptive", "UIUC-IMMCYC")

# for converting projection-horizon week to epi week
proj_week_dates = proj_start_date + (0:51)*7
proj_MMWR = MMWRweek(proj_week_dates)

palette <- c("#e89f00", "#019e72", "#322288", "#57b4e9", "#f1e541", "#cc79a7","#d55e00","#0472b2")

```

## Initial analysis of individual scenarios

```{r}

# --- Initial analysis of individual scenarios -------------------------

for (ii in 1:5) {
  scenario = scenarios[ii]
  # plotting filename/path
  filename_median = file.path(plot_path, paste0("Nat_wave_prop_medianW", scenario, ".png"))
  filename = file.path(plot_path, paste0("Nat_wave_prop", scenario, ".png"))
  
  # extract national hospitalization trajectories
  df <- arrow::open_dataset(paste0(repo_path, folder_path), schema = schema,
                            partitioning = c("origin_date", "model_id", 
                                             "target", "location")) |>
    dplyr::filter(output_type == "sample", 
                  origin_date == "2025-04-27", scenario_id == scenario_ids[ii],
                  target == "inc hosp", age_group == "0-130") |>
    dplyr::collect()
  
  # find a median week for each trajectory
  df_median_horizon <- df %>%
    group_by(model_id, output_type_id, location) %>%
    arrange(horizon, .by_group = TRUE) %>%  # Ensure values are in horizon order
    mutate(
      cum_value = cumsum(value),
      total_value = sum(value),
      prop_cum = cum_value / total_value
    ) %>%
    filter(prop_cum >= 0.5) %>%
    slice_min(prop_cum, with_ties = FALSE) %>%
    select(model_id, output_type_id, location, median_horizon = horizon, cumulative_value = cum_value)
  
  # convert horizon week to MMWR epi week
  df_median_horizon$ew = proj_MMWR$MMWRweek[df_median_horizon$median_horizon]
  
  # up-sample models so they all have 300 results
  # Split into rows to repeat 
  to_repeat <- df_median_horizon %>%
    filter(model_id %in% upsamp_mods)
  
  repeated_rows <- to_repeat[rep(seq_len(nrow(to_repeat)), each = 3), ]
  
  # Combine with unmodified rows
  df_median_upsamp <- bind_rows(
    df_median_horizon %>% filter(!model_id %in% upsamp_mods),
    repeated_rows
  )
  
  # plot all trajectory medians
  tick_seq = seq(from=1, to=52, by=3)
  p1 = ggplot(df_median_upsamp %>% 
                filter(location == "US") %>%
                mutate(model_id = case_when(
                  model_id == "CFA-Scenarios" ~ "Model 1",
                  model_id == "JHU_UNC-flepiMoP" ~ "Model 2",
                  model_id == "MOBS_NEU-GLEAM_COVID" ~ "Model 3",
                  model_id == "PSI-M_CoV_2025" ~ "Model 4",
                  model_id == "UIUC-IMMCYC" ~ "Model 5",
                  model_id == "UNCC-Hierbin" ~ "Model 6",
                  model_id == "UT-ImmunoSEIRS" ~ "Model 7",
                  model_id == "UVA-adaptive" ~ "Model 8"
                ))
                , aes(x=median_horizon, fill=model_id)) +
    geom_histogram(binwidth=1, position="stack", boundary=0.5, closed="left") +
    scale_x_continuous(
      breaks = (1:52)[tick_seq],
      labels = proj_MMWR$MMWRweek[tick_seq]
    ) +
    scale_fill_manual("", values = palette) +
    labs(
      x="Median Hospitalization Week",
      y="Number of Trajectories",
      fill="Model",
      title=paste0("Median Hospitalization Week - Scenario ", scenario)
    ) +
    theme_minimal()
  
  ggsave(filename_median, p1, width = 20, height = 10, bg = "white")
  
  
  # arbitrarily declare EW 43 as the divider between summer and winter waves
  # cumulatives below 45% are 'winter', greater than 55% are 'summer', in
  # between is 'similar'
  
  # find proportion of cumulative at horizon==26
  df_prop_cum <- df %>%
    group_by(model_id, output_type_id, location) %>%
    arrange(horizon, .by_group = TRUE) %>%  # Ensure values are in horizon order
    mutate(
      cum_value = cumsum(value),
      total_value = sum(value),
      prop_cum = cum_value / total_value
    ) %>%
    filter(horizon == 26) %>%
    select(model_id, output_type_id, location, prop_cum=prop_cum)
  
  # up-sample models so they all have 300 results
  # Split into rows to repeat and others
  to_repeat <- df_prop_cum %>%
    filter(model_id %in% upsamp_mods)
  
  repeated_rows <- to_repeat[rep(seq_len(nrow(to_repeat)), each = 3), ]
  
  # Combine with unmodified rows
  df_prop_upsamp <- bind_rows(
    df_prop_cum %>% filter(!model_id %in% upsamp_mods),
    repeated_rows
  )
  
  # Do the actual binning
  breaks = c(0., 0.45, 0.55, 1.0000000001)
  labels = c("Winter", "Similar", "Summer")
  
  df_binned = df_prop_upsamp %>%
    mutate(bin = cut(prop_cum, breaks = breaks, labels = labels, right = FALSE)) %>%
    count(bin, model_id, location)  # Get counts per bin per model/location
  # reorder bin names for plotting
  df_binned$bin = factor(df_binned$bin, levels=rev(labels))
  
  df_binned_save <- df_binned %>% 
                left_join(read_csv("locations.csv"), by = "location") %>%
                mutate(abbreviation = fct_relevel(abbreviation, c("US"))) %>%
                mutate(model_id = case_when(
                  model_id == "CFA-Scenarios" ~ "Model 1",
                  model_id == "JHU_UNC-flepiMoP" ~ "Model 2",
                  model_id == "MOBS_NEU-GLEAM_COVID" ~ "Model 3",
                  model_id == "PSI-M_CoV_2025" ~ "Model 4",
                  model_id == "UIUC-IMMCYC" ~ "Model 5",
                  model_id == "UNCC-Hierbin" ~ "Model 6",
                  model_id == "UT-ImmunoSEIRS" ~ "Model 7",
                  model_id == "UVA-adaptive" ~ "Model 8"
                ))
  
  write_csv(df_binned_save, paste("data/binned_locations_scenario_", scenario, ".csv", sep = ""))
  
  p2 = ggplot(df_binned %>%
                left_join(read_csv("locations.csv"), by = "location") %>%
                mutate(abbreviation = fct_relevel(abbreviation, c("US"))) %>%
                mutate(model_id = case_when(
                  model_id == "CFA-Scenarios" ~ "Model 1",
                  model_id == "JHU_UNC-flepiMoP" ~ "Model 2",
                  model_id == "MOBS_NEU-GLEAM_COVID" ~ "Model 3",
                  model_id == "PSI-M_CoV_2025" ~ "Model 4",
                  model_id == "UIUC-IMMCYC" ~ "Model 5",
                  model_id == "UNCC-Hierbin" ~ "Model 6",
                  model_id == "UT-ImmunoSEIRS" ~ "Model 7",
                  model_id == "UVA-adaptive" ~ "Model 8"
                ))
                ,
                #filter(location == "US"), 
              aes(x = bin, y = n, fill = model_id)) +
    facet_wrap(~abbreviation) + 
    geom_col(position = "stack") +
    scale_fill_manual("", values = palette) +
    labs(
      x = "EW 43 Cumulative Proportion",
      y = "Number of Trajectories",
      fill = "Model",
      title = paste0("EW 43 Cumulative Proportion - Scenario ", scenario)
    ) +
    theme_minimal()
  
  ggsave(filename, p2, width = 20, height = 10, bg = "white")
}

```



## Aggregate bars per location
```{r}

## code to generate file for piecharts in Figure S8

location_aggregated_bars <- read_csv("data/binned_locations_scenario_A.csv") %>%
  group_by(location_name, abbreviation, bin) %>%
  reframe(count_bins = sum(n)) %>%
  ungroup() %>%
  group_by(location_name, abbreviation) %>%
  mutate(count_total = sum(count_bins)) %>%
  ungroup() %>%
  mutate(proportion_bins = count_bins/count_total)

write_csv(location_aggregated_bars, "data/location_bins_Scenario_A_for_piechart.csv")

```


## Now repeat, comparing scenario totals to counterfactual
```{r}


# --- Now repeat, comparing scenario totals to counterfactual --------------
ii = 1
scenario = scenarios[ii]

df <- arrow::open_dataset(paste0(repo_path, folder_path), schema = schema,
                          partitioning = c("origin_date", "model_id", 
                                           "target", "location")) |>
  dplyr::filter(output_type == "sample",  
                origin_date == "2025-04-27", scenario_id == scenario_ids[ii],
                target == "inc hosp", age_group == "0-130") |>
  dplyr::collect()


# arbitrarily declare EW 43 as the divider between summer and winter waves
# cumulatives below 40% are 'summer', greater than 40% are 'winter'

# find proportion of cumulative at horizon==26
df_prop_cum_a <- df %>%
  group_by(model_id, output_type_id, location) %>%
  arrange(horizon, .by_group = TRUE) %>%  # Ensure values are in horizon order
  mutate(
    cum_value = cumsum(value),
    total_value = sum(value),
    prop_cum = cum_value / total_value
  ) %>%
  mutate(half_week = if_else(
    prop_cum >= 0.5, "Post", "Pre")
    ) %>%
  ## want the minimum week in the Post group 
  group_by(model_id, output_type_id, location, half_week) %>%
  ## group by half_week and if we are in the half_week == Post group, then set it to minimum horizon of that group
  ## If we are in the Pre group, set it to -1
  mutate(half_week2 = if_else(half_week == "Post", min(horizon), -1)) %>%
  ungroup() %>%
  group_by(model_id, output_type_id, location) %>%
  ## then grab the max across both pre/post, which will return min of post
  mutate(median_horizon = max(half_week2)) %>%
  filter(horizon == 26) %>%
  select(model_id, output_type_id, location, prop_cum=prop_cum, median_horizon, tot=total_value)

# up-sample models so they all have 300 results
# Split into rows to repeat and others
to_repeat <- df_prop_cum_a %>%
  filter(model_id %in% upsamp_mods)

repeated_rows <- to_repeat[rep(seq_len(nrow(to_repeat)), each = 3), ]

# Combine with unmodified rows
df_prop_upsamp_a <- bind_rows(
  df_prop_cum_a %>% filter(!model_id %in% upsamp_mods),
  repeated_rows
)

breaks = c(0., 0.45, 0.55, 1.0000000001)
labels = c("Winter", "Similar", "Summer")

df_binned_a = df_prop_upsamp_a %>%
  mutate(bin = cut(prop_cum, breaks = breaks, labels = labels, right = FALSE)) 
#   %>% count(bin, model_id)  # Get counts per bin per model

df_binned = df_prop_upsamp_a %>%
  mutate(bin = cut(prop_cum, breaks = breaks, labels = labels, right = FALSE)) %>% 
  count(bin, model_id, location)  # Get counts per bin per model/location

p2 = ggplot(df_binned %>% filter(location == "US") %>%
              mutate(model_id = case_when(
                model_id == "CFA-Scenarios" ~ "Model 1",
                model_id == "JHU_UNC-flepiMoP" ~ "Model 2",
                model_id == "MOBS_NEU-GLEAM_COVID" ~ "Model 3",
                model_id == "PSI-M_CoV_2025" ~ "Model 4",
                model_id == "UIUC-IMMCYC" ~ "Model 5",
                model_id == "UNCC-Hierbin" ~ "Model 6",
                model_id == "UT-ImmunoSEIRS" ~ "Model 7",
                model_id == "UVA-adaptive" ~ "Model 8"
              ))
              , aes(x = bin, y = n, fill = model_id)) +
  geom_col(position = "stack") +
  scale_fill_manual("", values = palette) +
  labs(
    x = "EW 43 Cumulative Proportion",
    y = "Number of Trajectories",
    fill = "Model",
    title = paste0("EW 43 Cumulative Proportion - Scenario ", scenario)
  ) +
  theme_minimal()


for (ii in 2:5) {
  scenario = scenarios[ii]
  df <- arrow::open_dataset(paste0(repo_path, folder_path), schema = schema,
                            partitioning = c("origin_date", "model_id", 
                                             "target", "location")) |>
    dplyr::filter(output_type == "sample",  
                  origin_date == "2025-04-27", scenario_id == scenario_ids[ii],
                  target == "inc hosp", age_group == "0-130") |>
    dplyr::collect()
  
  #load_time = Sys.time() - start_time
  
  # arbitrarily declare EW 43 as the divider between summer and winter waves
  # cumulatives below 40% are 'summer', greater than 40% are 'winter'
  
  # find proportion of cumulative at horizon==26
  df_prop_cum_temp <- df %>%
    group_by(model_id, output_type_id, location) %>%
    arrange(horizon, .by_group = TRUE) %>%  # Ensure values are in horizon order
    mutate(
      cum_value = cumsum(value),
      total_value = sum(value),
      prop_cum = cum_value / total_value
    ) %>%
    mutate(half_week = if_else(
      prop_cum >= 0.5, "Post", "Pre")
    ) %>%
    ## want the minimum week in the Post group 
    group_by(model_id, output_type_id, location, half_week) %>%
    ## group by half_week and if we are in the half_week == Post group, then set it to minimum horizon of that group
    ## If we are in the Pre group, set it to -1
    mutate(half_week2 = if_else(half_week == "Post", min(horizon), -1)) %>%
    ungroup() %>%
    group_by(model_id, output_type_id, location) %>%
    ## then grab the max across both pre/post, which will return min of post
    mutate(median_horizon = max(half_week2)) %>%
    filter(horizon == 26) %>%
    select(model_id, output_type_id, location, prop_cum=prop_cum, median_horizon, tot=total_value)
  
  # up-sample models so they all have 300 results
  # Split into rows to repeat and others
  to_repeat <- df_prop_cum_temp %>%
    filter(model_id %in% upsamp_mods)
  
  repeated_rows <- to_repeat[rep(seq_len(nrow(to_repeat)), each = 3), ]
  
  # Combine with unmodified rows
  df_prop_upsamp_temp <- bind_rows(
    df_prop_cum_temp %>% filter(!model_id %in% upsamp_mods),
    repeated_rows
  )
  
  breaks = c(0., 0.45, 0.55, 1.0000000001)
  labels = c("Winter", "Similar", "Summer")
  
  df_binned_temp = df_prop_upsamp_temp %>%
    mutate(bin = cut(prop_cum, breaks = breaks, labels = labels, right = FALSE)) 
  
  var_name_base = paste0("scen", scenario, "_")
  df_prop_upsamp_a[[paste0(var_name_base, "tot")]] = df_prop_upsamp_temp$tot
  df_binned_a[[paste0(var_name_base, "bin")]] = df_binned_temp$bin
}

# add columns for the difference between B/C and D/E
df_prop_upsamp_a[["diff_BC"]] = df_prop_upsamp_a$scenC_tot - df_prop_upsamp_a$scenB_tot
df_prop_upsamp_a[["diff_DE"]] = df_prop_upsamp_a$scenE_tot - df_prop_upsamp_a$scenD_tot

# now loop through B to E and collect relative averted
df_averted = df_prop_upsamp_a[, 1:4]
df_averted_long = data.frame(scenario=character(), timing=character(),
                             location = character(),
                             model_id = character(),
                             prop_cum = numeric(),
                             median_horizon = numeric(),
                             rel_vec_perc=numeric())

## for each of B-E
for (ii in 2:5) {
  scenario = scenarios[ii]
  
  rel_avert = (df_prop_upsamp_a$tot - 
                 df_prop_upsamp_a[[paste0("scen", scenario, "_tot")]])/df_prop_upsamp_a$tot
  df_averted[[scenario]] = rel_avert
  
  ## for each wave timing
  for (jj in 3:1) {
    timing_label = labels[jj]
    timing_index = df_binned_a$bin == timing_label
    rel_vec = as.vector(unlist(df_averted[timing_index, scenario]))
    rel_vec_perc = rel_vec*100
    
    location <- df_binned_a[df_binned_a$bin == timing_label, ]$location
    model_id <- df_binned_a[df_binned_a$bin == timing_label, ]$model_id
    prop_cum <- df_binned_a[df_binned_a$bin == timing_label, ]$prop_cum
    median_horizon <- df_binned_a[df_binned_a$bin == timing_label, ]$median_horizon
    

    df_averted_long = rbind(df_averted_long, 
                            data.frame(scenario=scenario, 
                                       timing=timing_label,
                                       location = location,
                                       model_id = model_id,
                                       prop_cum = prop_cum,
                                       median_horizon = median_horizon,
                                       rel_vec_perc=rel_vec_perc))
  }
}



# add columns for the relative difference between B/C and D/E
df_averted[["diff_BC"]] = df_averted$C - df_averted$B
df_averted[["diff_DE"]] = df_averted$E - df_averted$D

# convert timing column to a factor to preserve ordering in plots
df_averted_long$timing = factor(df_averted_long$timing, 
                                levels = unique(df_averted_long$timing))

# for each scenario, make an averted plot by timing - Summer, Similar, Winter 
y_lims = c(0, 50)
p_avert = list()
for (jj in 2:5) {
  scenario = scenarios[jj]
  
  scen_df = df_averted_long[df_averted_long$scenario==scenario, ]
  p_avert[[scenario]] = ggplot(scen_df %>% filter(location == "US")
                                 , aes(x=timing, y=rel_vec_perc)) +
    geom_boxplot() +
    coord_flip(ylim = y_lims) +  # flip axes to make horizontal
    theme_minimal() +
    labs(x="Timing", y="Percent Hospital Admissions Averted", 
         title = paste0("Scenario ", scenario))
  
  
}


combined_plot = p_avert$B / p_avert$C / p_avert$D / p_avert$E
filename = file.path(plot_path, "Nat_avert_timing.png")
ggsave(filename, combined_plot, width = 14, height = 30)



# Collapse these plots into C vs B, and E vs D
df_averted_diff_long = data.frame(scenario=character(), timing=character(), 
                                  location = character(),
                                  model_id = character(),
                                  prop_cum = numeric(),
                                  median_horizon = numeric(),
                                  rel_vec_perc=numeric())
slice_names = c("diff_BC", "diff_DE")
for (ii in c(2, 4)) {
  slice = slice_names[ii/2]
  rel_avert = df_averted[[slice]]
  for (jj in 3:1) {
    timing_label = labels[jj]
    timing_index = df_binned_a$bin == timing_label
    rel_vec_perc = rel_avert[timing_index]*100
    
    location <- df_binned_a[df_binned_a$bin == timing_label, ]$location
    model_id <- df_binned_a[df_binned_a$bin == timing_label, ]$model_id
    prop_cum <- df_binned_a[df_binned_a$bin == timing_label, ]$prop_cum
    median_horizon <- df_binned_a[df_binned_a$bin == timing_label, ]$median_horizon
    
    
    
    
    df_averted_diff_long = rbind(df_averted_diff_long, 
                                 data.frame(scenario=slice, timing=timing_label,
                                            location =location,
                                            model_id = model_id,
                                            prop_cum = prop_cum,
                                            median_horizon = median_horizon,
                                            rel_vec_perc=rel_vec_perc))
  }
}

# convert timing column to a factor to preserve ordering in plots
df_averted_diff_long$timing = factor(df_averted_diff_long$timing, 
                                     levels = unique(df_averted_diff_long$timing))

# for each scenario comparison, make an averted plot by timing - Summer, Similar, Winter 
y_lims = c(-15, 15)
p_diff_avert = list()
for (jj in 1:2) {
  slice = slice_names[jj]
  
  if (jj==1) {
    title = "Difference Percent Averted (C-B)/A"
  } else if (jj==2) {
    title = "Difference Percent Averted (E-D)/A"
  }
  
  scen_df = df_averted_diff_long[df_averted_diff_long$scenario==slice, ]
  p_diff_avert[[slice]] = ggplot(scen_df %>% filter(location == "US"), aes(x=timing, y=rel_vec_perc)) +
    geom_boxplot() +
    coord_flip(ylim = y_lims) +  # flip axes to make horizontal
    #coord_flip() +
    theme_minimal() +
    labs(x="Timing", y="Percent Hospital Admissions Averted", 
         title = title)
  
  
}

combined_plot = p_diff_avert$diff_BC / p_diff_avert$diff_DE
filename = file.path(plot_path, "Nat_avert_compare_timing.png")
ggsave(filename, combined_plot, width = 14, height = 20)

```

## Reassign model names and save data

```{r}
# -------- Reassign model names and save data -----------------

df_averted_long <- df_averted_long %>%
  mutate(model_id = case_when(
    model_id == "CFA-Scenarios" ~ "Model 1",
    model_id == "JHU_UNC-flepiMoP" ~ "Model 2",
    model_id == "MOBS_NEU-GLEAM_COVID" ~ "Model 3",
    model_id == "PSI-M_CoV_2025" ~ "Model 4",
    model_id == "UIUC-IMMCYC" ~ "Model 5",
    model_id == "UNCC-Hierbin" ~ "Model 6",
    model_id == "UT-ImmunoSEIRS" ~ "Model 7",
    model_id == "UVA-adaptive" ~ "Model 8"
  ))
write_csv(df_averted_long, "data/df_averted_long.csv")

df_averted_diff_long <- df_averted_diff_long %>%
  mutate(model_id = case_when(
    model_id == "CFA-Scenarios" ~ "Model 1",
    model_id == "JHU_UNC-flepiMoP" ~ "Model 2",
    model_id == "MOBS_NEU-GLEAM_COVID" ~ "Model 3",
    model_id == "PSI-M_CoV_2025" ~ "Model 4",
    model_id == "UIUC-IMMCYC" ~ "Model 5",
    model_id == "UNCC-Hierbin" ~ "Model 6",
    model_id == "UT-ImmunoSEIRS" ~ "Model 7",
    model_id == "UVA-adaptive" ~ "Model 8"
  ))
write_csv(df_averted_diff_long, "data/df_averted_diff_long.csv")

```


## Scenario/model/location regression analysis 
```{r}
######## Regression analysis ########

list_of_scenario_model_location <- df_averted_long %>%
  select(model_id, scenario, location) %>%
  distinct()


states_regression <- NULL

for (i in 1:nrow(list_of_scenario_model_location)){
  ## set scenario, model, location combination
  scenario2 <- list_of_scenario_model_location$scenario[i]
  model_id2 <- list_of_scenario_model_location$model_id[i]
  location2 <- list_of_scenario_model_location$location[i]
  ## filter
  df_states_regression <- df_averted_long %>%
    filter(scenario == scenario2, model_id == model_id2, location == location2)# %>%
    #filter(model_id == "UT-ImmunoSEIRS", location == "02", scenario == "B")
  ## run linear regression, rel averted response to median horizon
  model <- lm(rel_vec_perc ~ median_horizon, data = df_states_regression)
  ## tidy model and pull coefficient
  x <- tidy(model) %>% filter(term == "median_horizon") %>%
    select(estimate)
  ## create corresponding row in data frame
  df_states_regression <- tibble(scenario = scenario2, model_id = model_id2, location = location2, coeff = x$estimate[1])
  ## add to states regression
  states_regression <- states_regression %>% rbind(df_states_regression)
}

write_csv(states_regression, "data/states_regression.csv")


list_of_scenario_model_location_diff <- df_averted_diff_long %>%
  select(model_id, scenario, location) %>%
  distinct()

states_regression_diff <- NULL

for (i in 1:nrow(list_of_scenario_model_location_diff)){
  ## set scenario, model, location combination
  scenario2 <- list_of_scenario_model_location_diff$scenario[i]
  model_id2 <- list_of_scenario_model_location_diff$model_id[i]
  location2 <- list_of_scenario_model_location_diff$location[i]
  ## filter
  df_states_regression_diff <- df_averted_diff_long %>%
    filter(scenario == scenario2, model_id == model_id2, location == location2)
  ## run linear regression, rel averted response to median horizon
  model <- lm(rel_vec_perc ~ median_horizon, data = df_states_regression_diff)
  ## tidy model and pull coefficient
  x <- tidy(model) %>% filter(term == "median_horizon") %>%
    select(estimate)
  ## create corresponding row in data frame
  df_states_regression_diff <- tibble(scenario = scenario2, model_id = model_id2, location = location2, coeff = x$estimate[1])
  ## add to states regression
  states_regression_diff <- states_regression_diff %>% rbind(df_states_regression_diff)
}

write_csv(states_regression_diff, "data/states_regression_diff.csv")

```

## Figures
### Percent averted by model
```{r}
palette <- c("#e89f00", "#019e72", "#322288", "#57b4e9", "#f1e541", "#cc79a7","#d55e00","#0472b2")

## --- Percent averted -------------------------
# test <- df_averted_diff_long %>% select(scenario, timing, location, model_id, rel_vec_perc, prop_cum) %>% filter(location == "US") %>% distinct() %>%  mutate(count = 1) %>% group_by(scenario, timing, location, model_id) %>% summarise(countall = sum(count)) %>% ungroup()
plot_model_segregation <- ggplot(df_averted_long %>% filter(location == "US", !(model_id == "UIUC-IMMCYC" & location == "US"& timing == "Winter")), aes(x=timing, y=rel_vec_perc)) +
  geom_boxplot() +
  coord_flip() +  # flip axes to make horizontal
  #coord_flip() +
  theme_minimal() +
  facet_grid(scenario~model_id) + 
  theme(panel.border = element_blank(), axis.line = element_line()) + 
  labs(x="Timing", y="Percent Hospital Admissions Averted", 
       title = "Percent Averted") 
plot_model_segregation

filename = file.path(plot_path, "Scenarios_by_model.png")
ggsave(filename, plot_model_segregation, width = 14, height = 5)

## --- Difference percent averted -------------------------
# test <- df_averted_diff_long %>% select(scenario, timing, location, model_id, rel_vec_perc, prop_cum) %>% filter(location == "US") %>%  mutate(count = 1) %>% group_by(scenario, timing, location, model_id) %>% summarise(countall = sum(count)) %>% ungroup()
plot_model_segregationA <- ggplot(df_averted_diff_long %>% filter(location == "US", scenario == "diff_BC", !(model_id == "UIUC-IMMCYC" & location == "US"& timing == "Winter")), aes(x=timing, y=rel_vec_perc)) +
  geom_boxplot() +
  coord_flip(ylim = y_lims) +  # flip axes to make horizontal
  #coord_flip() +
  theme_minimal() +
  facet_wrap(~model_id) + 
  theme(panel.border = element_blank(), axis.line = element_line()) + 
  labs(x="Timing", y="Percent Hospital Admissions Averted", 
       title = "Difference Percent Averted (C-B)/A") 
plot_model_segregationA
plot_model_segregationB <- ggplot(df_averted_diff_long %>% filter(location == "US", scenario == "diff_DE", !(model_id == "UIUC-IMMCYC" & location == "US"& timing == "Winter")), aes(x=timing, y=rel_vec_perc)) +
  geom_boxplot() +
  coord_flip(ylim = y_lims) +  # flip axes to make horizontal
  #coord_flip() +
  theme_minimal() +
  facet_wrap(~model_id) + 
  theme(panel.border = element_blank(), axis.line = element_line()) + 
  labs(x="Timing", y="Percent Hospital Admissions Averted", 
       title = "Difference Percent Averted (E-D)/A") 
plot_model_segregationB

combined_plot = plot_model_segregationA / plot_model_segregationB
filename = file.path(plot_path, "Nat_avert_compare_timing_by_model.png")
ggsave(filename, combined_plot, width = 7, height = 10)


```

### Difference percent averted by locations
```{r}

## --- LOCATIONS difference percent averted -------------------------
# test <- df_averted_diff_long %>% select(scenario, timing, location, model_id, rel_vec_perc, prop_cum) %>% filter(location == "US") %>%  mutate(count = 1) %>% group_by(scenario, timing, location, model_id) %>% summarise(countall = sum(count)) %>% ungroup()
plot_model_segregationA <- ggplot(df_averted_diff_long %>% filter(location != "US", scenario == "diff_BC") %>% left_join(read_csv("locations.csv"), by = c("location")) %>%
                                    mutate(abbreviation = fct_relevel(abbreviation, c("US"))), aes(x=timing, y=rel_vec_perc)) +
  geom_boxplot() +
  coord_flip(ylim = y_lims) +  # flip axes to make horizontal
  #coord_flip() +
  theme_minimal() +
  facet_wrap(~abbreviation) + 
  theme(panel.border = element_blank(), axis.line = element_line()) + 
  labs(x="Timing", y="Percent Hospital Admissions Averted", 
       title = "Difference Percent Averted (C-B)/A") 
plot_model_segregationA
plot_model_segregationB <- ggplot(df_averted_diff_long %>% filter(location != "US", scenario == "diff_DE") %>% left_join(read_csv("locations.csv"), by = c("location")) %>%
                                    mutate(abbreviation = fct_relevel(abbreviation, c("US"))), aes(x=timing, y=rel_vec_perc)) +
  geom_boxplot() +
  coord_flip(ylim = y_lims) +  # flip axes to make horizontal
  #coord_flip() +
  theme_minimal() +
  facet_wrap(~abbreviation) + 
  theme(panel.border = element_blank(), axis.line = element_line()) + 
  labs(x="Timing", y="Percent Hospital Admissions Averted", 
       title = "Difference Percent Averted (E-D)/A") 
plot_model_segregationB

combined_plot = plot_model_segregationA / plot_model_segregationB
filename = file.path(plot_path, "Nat_avert_compare_timing_by_location.png")
ggsave(filename, combined_plot, width = 9, height = 15)


```


### Continuous wave timing scatterplot
```{r}

## --- Continuous scatterplot  -------------------------

## generate axis labels
## median horizon week to MMWR week
## MMWRweek(proj_start_date + 7*median_horizon)$MMWRweek

plot_continuous2 <- ggplot(df_averted_long %>% 
                             filter(location == "US") %>%
                             mutate(scenario = paste("Scenario ", scenario, sep = "")),
                           aes(x= median_horizon, y=rel_vec_perc, color = model_id, fill = model_id)) +
  geom_point(aes(color = model_id), alpha = 0.1) + 
  facet_wrap(~scenario) + 
  theme_minimal() +
  stat_poly_line(aes(color = model_id)) +
  scale_x_continuous(limits = c(10,50), breaks = seq(10,50, by = 4), labels = MMWRweek(proj_start_date + 7*seq(10,50, by = 4))$MMWRweek) + 
  labs(x="Median Hospitalization Week", y="Percent Hospital Admissions Averted", 
                                                       title = "Percent averted by scenario") +
  scale_fill_manual("", values = palette) +
  scale_color_manual("", values = palette) +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.5),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black"),
        plot.title = element_text(colour = "black", size = 13.5, face = "bold"),
        plot.title.position = "plot",
        plot.subtitle = element_text(colour = "black", size = 12.5),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        legend.position = "right",
        legend.margin=margin(1,1.5,0.5,0.5,unit = "line"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        strip.text = element_text(colour = "black", size = 12, hjust = 0),
        strip.background = element_rect(colour="white", fill="white"),
        panel.border = element_rect(colour = NA, fill=NA),
        panel.spacing = unit(0.5, "cm"), aspect.ratio=1)
plot_continuous2

filename = file.path(plot_path, "Nat_avert_continuous_timing_by_scenario.jpg")
ggsave(filename, plot_continuous2, width = 10, height = 8)


```

### Continuous wave timing difference
```{r}
## --- Continuous diff scatterplot -------------------------

plot_continuousA <- ggplot(df_averted_diff_long %>% 
                             filter(location == "US", scenario == "diff_BC") %>%
                             mutate(wave_type = if_else(model_id %in% c("Model 3", "Model 7"), "No summer wave", "Summer wave")), #, model_id != "MOBS_NEU-GLEAM_COVID", model_id != "UT-ImmunoSEIRS"),
                           aes(x=median_horizon, y=rel_vec_perc, color = model_id, fill = model_id)) +
  geom_point(aes(color = model_id), alpha = 0.1) +   
  theme_minimal() +
  stat_poly_line(aes(color = model_id)) +
  geom_hline(aes(yintercept = 0), color = "black", linetype = "dashed") + 
  # stat_poly_eq(use_label(c("eq","R2", "p")),
  #              geom = "label_npc", size = 2.5,
  #              color = "black",
  #              label.size = 0,
  #              alpha = 0.3
  # ) +
  labs(x="Median Hospitalization Week", y="Difference in Percent\nHospital Admissions Averted") +
  scale_x_continuous(limits = c(10,50), breaks = seq(10,50, by = 4), labels = MMWRweek(proj_start_date + 7*seq(10,50, by = 4))$MMWRweek) + 
  ggtitle("Difference Percent Averted", "Relative difference in\nscenarios (C-B)/A") + 
  facet_wrap(~wave_type) + 
  scale_fill_manual("", values = palette) +
  scale_color_manual("", values = palette) +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.5),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black"),
        plot.title = element_text(colour = "black", size = 13.5, face = "bold"),
        plot.title.position = "plot",
        plot.subtitle = element_text(colour = "black", size = 12.5),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        legend.position = "bottom",
        legend.margin=margin(1,1.5,0.5,0.5,unit = "line"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        strip.text = element_text(colour = "black", size = 12, hjust = 0),
        strip.background = element_rect(colour="white", fill="white"),
        panel.border = element_rect(colour = NA, fill=NA),
        panel.spacing = unit(0.5, "cm"), aspect.ratio=0.75)
plot_continuousA


plot_continuousB <- ggplot(df_averted_diff_long %>% 
                             filter(location == "US", scenario == "diff_DE") %>%
                             mutate(wave_type = if_else(model_id %in% c("Model 3", "Model 7"), "No summer wave", "Summer wave")), #, model_id != "MOBS_NEU-GLEAM_COVID", model_id != "UT-ImmunoSEIRS"), 
                           aes(x=median_horizon, y=rel_vec_perc, color = model_id, fill = model_id)) +
  geom_point(aes(color = model_id), alpha = 0.1) +  
  theme_minimal() +
  stat_poly_line(aes(color = model_id)) +
  geom_hline(aes(yintercept = 0), color = "black", linetype = "dashed") + 
  # stat_poly_eq(use_label(c("eq","R2", "p")),
  #              geom = "label_npc", size = 2.5,
  #              color = "black",
  #              label.size = 0,
  #              alpha = 0.3
  # ) +  
  labs(x="Median Hospitalization Week", y="Difference in Percent\nHospital Admissions Averted") + 
  scale_x_continuous(limits = c(10,50), breaks = seq(10,50, by = 4), labels = MMWRweek(proj_start_date + 7*seq(10,50, by = 4))$MMWRweek) + 
  ggtitle("", "Relative difference in\nscenarios (E-D)/A") +
  scale_fill_manual("", values = palette) +
  scale_color_manual("", values = palette) +
  facet_wrap(~wave_type) + 
  #scale_fill_manual("Model", values = c("#66c2a5", "#fc8d62", "#e78ac3", "#a6d854", "#ffd92f", "#b3b3b3")) + 
  #scale_color_manual("Model", values = c("#66c2a5", "#fc8d62", "#e78ac3", "#a6d854", "#ffd92f", "#b3b3b3")) + 
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.5),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black"),
        plot.title = element_text(colour = "black", size = 13.5, face = "bold"),
        plot.title.position = "plot",
        plot.subtitle = element_text(colour = "black", size = 12.5),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        legend.position = "none",
        legend.margin=margin(1,1.5,0.5,0.5,unit = "line"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        strip.text = element_text(colour = "black", size = 12, hjust = 0),
        strip.background = element_rect(colour="white", fill="white"),
        panel.border = element_rect(colour = NA, fill=NA),
        panel.spacing = unit(0.5, "cm"), aspect.ratio=0.75)
plot_continuousB




combined_plot = plot_continuousA / plot_continuousB
filename = file.path(plot_path, "Nat_avert_continuous_timing_by_model.jpg")
ggsave(filename, combined_plot, width = 7, height = 9)


```


### Continuous wave timing single regression
```{r}

## --- Continuous scatterplot  -------------------------

## generate axis labels
## median horizon week to MMWR week
## MMWRweek(proj_start_date + 7*median_horizon)$MMWRweek

plot_continuous2_singleregression <- ggplot(df_averted_long %>% 
                             filter(location == "US") %>%
                             mutate(scenario = paste("Scenario ", scenario, sep = "")),
                           aes(x= median_horizon, y=rel_vec_perc)) +
  geom_point(aes(color = model_id), alpha = 0.1) + 
  facet_wrap(~scenario) + 
  theme_minimal() +
  #stat_poly_line(color = "black", fill = "grey") +
  geom_smooth(color = "black", fill = "grey") + 
  scale_x_continuous(limits = c(10,50), breaks = seq(10,50, by = 4), labels = MMWRweek(proj_start_date + 7*seq(10,50, by = 4))$MMWRweek) + 
  labs(x="Median Hospitalization Week", y="Percent Hospital Admissions Averted", 
                                                       title = "Percent averted by scenario") +
  scale_fill_manual("", values = palette) +
  scale_color_manual("", values = palette) +
  guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.5),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black"),
        plot.title = element_text(colour = "black", size = 13.5, face = "bold"),
        plot.title.position = "plot",
        plot.subtitle = element_text(colour = "black", size = 12.5),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        legend.position = "right",
        legend.margin=margin(1,1.5,0.5,0.5,unit = "line"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        strip.text = element_text(colour = "black", size = 12, hjust = 0),
        strip.background = element_rect(colour="white", fill="white"),
        panel.border = element_rect(colour = NA, fill=NA),
        panel.spacing = unit(0.5, "cm"), aspect.ratio=1)
plot_continuous2_singleregression

filename = file.path(plot_path, "Nat_avert_continuous_timing_by_scenario_singleregression.jpg")
ggsave(filename, plot_continuous2_singleregression, width = 10, height = 8)


```


### Continuous wave timing difference single regression
```{r}
## --- Continuous diff scatterplot -------------------------

plot_continuousA_singleregression <- ggplot(df_averted_diff_long %>% 
                             filter(location == "US", scenario == "diff_BC") %>%
                             mutate(wave_type = if_else(model_id %in% c("Model 3", "Model 7"), "No summer wave", "Summer wave")), #, model_id != "MOBS_NEU-GLEAM_COVID", model_id != "UT-ImmunoSEIRS"),
                           aes(x=median_horizon, y=rel_vec_perc)) +
  geom_point(aes(color = model_id), alpha = 0.1) +   
  theme_minimal() +
  #stat_poly_line(color = "black", fill = "grey") +
  geom_smooth(color = "black", fill = "grey") + 
  geom_hline(aes(yintercept = 0), color = "black", linetype = "dashed") + 
  # stat_poly_eq(use_label(c("eq","R2", "p")),
  #              geom = "label_npc", size = 2.5,
  #              color = "black",
  #              label.size = 0,
  #              alpha = 0.3
  # ) +
  labs(x="Median Hospitalization Week", y="Difference in Percent\nHospital Admissions Averted") +
  scale_x_continuous(limits = c(10,50), breaks = seq(10,50, by = 4), labels = MMWRweek(proj_start_date + 7*seq(10,50, by = 4))$MMWRweek) + 
  ggtitle("Difference Percent Averted", "Relative difference in\nscenarios (C-B)/A") + 
  guides(colour = guide_legend(override.aes = list(alpha = 1))) +
  facet_wrap(~wave_type, scales = "free") + 
  scale_fill_manual("", values = palette) +
  scale_color_manual("", values = palette) +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.5),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black"),
        plot.title = element_text(colour = "black", size = 13.5, face = "bold"),
        plot.title.position = "plot",
        plot.subtitle = element_text(colour = "black", size = 12.5),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        legend.position = "bottom",
        legend.margin=margin(1,1.5,0.5,0.5,unit = "line"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        strip.text = element_text(colour = "black", size = 12, hjust = 0),
        strip.background = element_rect(colour="white", fill="white"),
        panel.border = element_rect(colour = NA, fill=NA),
        panel.spacing = unit(0.5, "cm"), aspect.ratio=0.75)
plot_continuousA_singleregression


plot_continuousB_singleregression <- ggplot(df_averted_diff_long %>% 
                             filter(location == "US", scenario == "diff_DE") %>%
                             mutate(wave_type = if_else(model_id %in% c("Model 3", "Model 7"), "No summer wave", "Summer wave")), #, model_id != "MOBS_NEU-GLEAM_COVID", model_id != "UT-ImmunoSEIRS"), 
                           aes(x=median_horizon, y=rel_vec_perc)) +
  geom_point(aes(color = model_id), alpha = 0.1) +  
  theme_minimal() +
  #stat_poly_line(color = "black", fill = "grey") +
  geom_smooth(color = "black", fill = "grey") + 
  geom_hline(aes(yintercept = 0), color = "black", linetype = "dashed") + 
  # stat_poly_eq(use_label(c("eq","R2", "p")),
  #              geom = "label_npc", size = 2.5,
  #              color = "black",
  #              label.size = 0,
  #              alpha = 0.3
  # ) +  
  labs(x="Median Hospitalization Week", y="Difference in Percent\nHospital Admissions Averted") + 
  scale_x_continuous(limits = c(10,50), breaks = seq(10,50, by = 4), labels = MMWRweek(proj_start_date + 7*seq(10,50, by = 4))$MMWRweek) + 
  ggtitle("", "Relative difference in\nscenarios (E-D)/A") +
  scale_fill_manual("", values = palette) +
  scale_color_manual("", values = palette) +
  facet_wrap(~wave_type, scales = "free") + 
  #scale_fill_manual("Model", values = c("#66c2a5", "#fc8d62", "#e78ac3", "#a6d854", "#ffd92f", "#b3b3b3")) + 
  #scale_color_manual("Model", values = c("#66c2a5", "#fc8d62", "#e78ac3", "#a6d854", "#ffd92f", "#b3b3b3")) + 
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.5),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black"),
        plot.title = element_text(colour = "black", size = 13.5, face = "bold"),
        plot.title.position = "plot",
        plot.subtitle = element_text(colour = "black", size = 12.5),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        legend.position = "none",
        legend.margin=margin(1,1.5,0.5,0.5,unit = "line"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        strip.text = element_text(colour = "black", size = 12, hjust = 0),
        strip.background = element_rect(colour="white", fill="white"),
        panel.border = element_rect(colour = NA, fill=NA),
        panel.spacing = unit(0.5, "cm"), aspect.ratio=0.75)
plot_continuousB_singleregression




combined_plot_singleregression = plot_continuousA_singleregression / plot_continuousB_singleregression
filename = file.path(plot_path, "Nat_avert_continuous_timing_by_model_singleregression.jpg")
ggsave(filename, combined_plot_singleregression, width = 7, height = 9)


```


### Continuous w/ all locations
```{r}
####### Continuous with all locations ########

plot_continuous22 <- ggplot(df_averted_long %>% filter(location != "US") %>%
                             mutate(scenario = paste("Scenario ", scenario, sep = "")), #, model_id != "MOBS_NEU-GLEAM_COVID", model_id != "UT-ImmunoSEIRS"), 
                           aes(x=median_horizon, y=rel_vec_perc, color = model_id, fill = model_id)) +
  geom_point(color = "grey", alpha = 0.2) + 
  facet_wrap(~scenario) + 
  theme_minimal() +
  stat_poly_line() +
  # stat_poly_eq(use_label(c("eq","R2", "p")),
  # geom = "label_npc", size = 3,
  # label.size = 0,
  # alpha = 0.3
  # ) +
  labs(x="Median Hospitalization Week", y="Percent Hospital Admissions Averted", 
       title = "Percent averted by scenario") +
  scale_x_continuous(limits = c(1,50), breaks = seq(1,50, by = 4), labels = MMWRweek(proj_start_date + 7*seq(1,50, by = 4))$MMWRweek) + 
  scale_fill_manual("", values = palette) +
  scale_color_manual("", values = palette) +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.5),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black"),
        plot.title = element_text(colour = "black", size = 13.5, face = "bold"),
        plot.title.position = "plot",
        plot.subtitle = element_text(colour = "black", size = 12.5),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        legend.position = "right",
        legend.margin=margin(1,1.5,0.5,0.5,unit = "line"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        strip.text = element_text(colour = "black", size = 12, hjust = 0),
        strip.background = element_rect(colour="white", fill="white"),
        panel.border = element_rect(colour = NA, fill=NA),
        panel.spacing = unit(0.5, "cm"), aspect.ratio=1)
plot_continuous22

filename = file.path(plot_path, "Nat_avert_continuous_timing_all_locations.jpg")
ggsave(filename, plot_continuous22, width = 8, height = 6)


```


### Continuous difference (all locations)
```{r}
plot_continuousA2 <- ggplot(df_averted_diff_long %>% 
                             filter(location != "US", scenario == "diff_BC") %>%
                             mutate(wave_type = if_else(model_id %in% c("Model 3", "Model 7"), "No summer wave", "Summer wave")), #, model_id != "MOBS_NEU-GLEAM_COVID", model_id != "UT-ImmunoSEIRS"),
                           aes(x=median_horizon, y=rel_vec_perc, color = model_id, fill = model_id)) +
  geom_point(color = "grey", alpha = 0.2) +   
  theme_minimal() +
  stat_poly_line() +
  geom_hline(aes(yintercept = 0), color = "black", linetype = "dashed") + 
  # stat_poly_eq(use_label(c("eq","R2", "p")),
  #              geom = "label_npc", size = 2.5,
  #              label.size = 0,
  #              alpha = 0.3
  # ) +
  facet_wrap(~model_id, nrow = 2, scales = "free") + 
  labs(x="Median Hospitalization Week", y="Difference in Percent\nHospital Admissions Averted") +
  scale_x_continuous(limits = c(1,50), breaks = seq(1,50, by = 8), labels = MMWRweek(proj_start_date + 7*seq(1,50, by = 8))$MMWRweek) + 
  ggtitle("Difference Percent Averted", "Relative difference in\nscenarios (C-B)/A") + 
  scale_fill_manual("", values = palette) +
  scale_color_manual("", values = palette) +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.5),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black"),
        plot.title = element_text(colour = "black", size = 13.5, face = "bold"),
        plot.title.position = "plot",
        plot.subtitle = element_text(colour = "black", size = 12.5),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        legend.position = "bottom",
        legend.margin=margin(1,1.5,0.5,0.5,unit = "line"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        strip.text = element_text(colour = "black", size = 12, hjust = 0),
        strip.background = element_rect(colour="white", fill="white"),
        panel.border = element_rect(colour = NA, fill=NA),
        panel.spacing = unit(0.5, "cm"), aspect.ratio=0.75)
plot_continuousA2



plot_continuousB2 <- ggplot(df_averted_diff_long %>% 
                             filter(location != "US", scenario == "diff_DE") %>%
                             mutate(wave_type = if_else(model_id %in% c("MOBS_NEU-GLEAM_COVID", "UT-ImmunoSEIRS"), "No summer wave", "Summer wave")), #, model_id != "MOBS_NEU-GLEAM_COVID", model_id != "UT-ImmunoSEIRS"), 
                           aes(x=median_horizon, y=rel_vec_perc, color = model_id, fill = model_id)) +
  geom_point(color = "grey", alpha = 0.2) +  
  theme_minimal() +
  stat_poly_line() +
  geom_hline(aes(yintercept = 0), color = "black", linetype = "dashed") + 
  # stat_poly_eq(use_label(c("eq","R2", "p")),
  #              geom = "label_npc", size = 2.5,
  #              color = "black", fill = "grey",
  #              label.size = 0,
  #              alpha = 0.3
  # ) +
  facet_wrap(~model_id, nrow = 2, scales = "free") + 
  labs(x="Median Hospitalization Week", y="Difference in Percent\nHospital Admissions Averted") + 
  scale_x_continuous(limits = c(1,50), breaks = seq(1,50, by = 8), labels = MMWRweek(proj_start_date + 7*seq(1,50, by = 8))$MMWRweek) + 
  ggtitle("", "Relative difference in\nscenarios (E-D)/A") +
  scale_fill_manual("", values = palette) +
  scale_color_manual("", values = palette) +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.5),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black"),
        plot.title = element_text(colour = "black", size = 13.5, face = "bold"),
        plot.title.position = "plot",
        plot.subtitle = element_text(colour = "black", size = 12.5),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        legend.position = "none",
        legend.margin=margin(1,1.5,0.5,0.5,unit = "line"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        strip.text = element_text(colour = "black", size = 12, hjust = 0),
        strip.background = element_rect(colour="white", fill="white"),
        panel.border = element_rect(colour = NA, fill=NA),
        panel.spacing = unit(0.5, "cm"), aspect.ratio=0.75)
plot_continuousB2

combined_plot = plot_continuousA2 / plot_continuousB2
filename = file.path(plot_path, "Nat_avert_continuous_timing_all_locations_scenarios.jpg")
ggsave(filename, combined_plot, width = 9, height = 10)

```

### Coefficients by location
```{r}
#### Coeffs by location ####
plot_coefficients_by_location <- read_csv( "data/states_regression.csv") %>%
  mutate(model_id = gsub("Model ", "", model_id)) %>%
  #filter(model_id != "MOBS_NEU-GLEAM_COVID", model_id != "UT-ImmunoSEIRS") %>%
  filter(!is.na(coeff)) %>%
  left_join(read_csv("locations.csv"), by = c("location")) %>%
  mutate(abbreviation = fct_relevel(abbreviation, c("US"))) %>%
  ggplot(aes(x = abbreviation, y = model_id, fill = coeff)) + 
  geom_tile() + 
  scale_fill_stepsn("Slope",
                    colors = c("#f4a582", "#d1e5f0", "#92c5de", "#4393c3", "#2166ac", "#053061"),
                    n.breaks = 10
                       ) +
  facet_wrap(~scenario, nrow = 4) + 
  scale_x_discrete("Location", expand = c(0,0)) + 
  scale_y_discrete("Model", expand = c(0,0)) + 
  ggtitle("Percent averted vs. hospitalization week") + 
  theme_classic() + 
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        axis.text.x = element_text(angle = 90, vjust = 0.5, size = 10),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black"),
        plot.title = element_text(colour = "black", size = 13.5, face = "bold"),
        plot.title.position = "plot",
        plot.subtitle = element_text(colour = "black", size = 12.5),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        legend.position = "right",
        legend.margin=margin(1,1.5,1.5,1.5,unit = "line"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        strip.text = element_text(colour = "black", size = 12, hjust = 0),
        strip.background = element_rect(colour="white", fill="white"),
        panel.border = element_rect(colour = NA, fill=NA),
        panel.spacing = unit(0.5, "cm"), aspect.ratio=0.25)
plot_coefficients_by_location

filename = file.path(plot_path, "Nat_avert_continuous_timing_coefficient_matrix.jpg")
ggsave(filename, plot_coefficients_by_location, width = 12, height = 9)

## percentage with positive slope
test <- states_regression %>% 
  filter(location != "US") %>%
  filter(!is.na(coeff)) %>%
  mutate(slope_sign = if_else(coeff > 0, 1, 0),
         index = 1) %>%
  #group_by(scenario) %>%
  mutate(total = sum(index),
         pos = sum(slope_sign),
         perc_pos = 100*pos/total
         ) #%>%
  #select(perc_pos, scenario) %>% distinct()

```

### Coefficients (difference) by location
```{r}
#### Diff coeffs by location ####
plot_coefficients_by_location_diff <- read_csv("data/states_regression_diff.csv") %>%
  mutate(scenario = if_else(scenario == "diff_BC", "(C-B)/A", "(E-D)/A")) %>%
  mutate(model_id = gsub("Model ", "", model_id)) %>%
  #filter(model_id != "MOBS_NEU-GLEAM_COVID", model_id != "UT-ImmunoSEIRS") %>%
  filter(!is.na(coeff)) %>%
  left_join(read_csv("locations.csv"), by = c("location")) %>%
  mutate(abbreviation = fct_relevel(abbreviation, c("US"))) %>%
  ggplot(aes(x = abbreviation, y = model_id, fill = coeff)) + 
  geom_tile() + 
  scale_fill_stepsn("Slope",
                    colors = c("#67001f","#b2182b","#d6604d","#f4a582", "#d1e5f0", "#92c5de", "#4393c3", "#2166ac", "#053061"),
                    n.breaks = 10
  ) +
  facet_wrap(~scenario, nrow = 2) + 
  scale_x_discrete("Location", expand = c(0,0)) + 
  scale_y_discrete("Model", expand = c(0,0)) + 
  ggtitle("Percent averted vs. hospitalization week") + 
  theme_classic() + 
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 12, color = "black"),
        axis.text.x = element_text(angle = 90, vjust = 0.5, size = 10),
        axis.line = element_line(color = "black"),
        axis.ticks = element_line(color = "black"),
        plot.title = element_text(colour = "black", size = 13.5, face = "bold"),
        plot.title.position = "plot",
        plot.subtitle = element_text(colour = "black", size = 12.5),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"),
        legend.position = "right",
        legend.margin=margin(1,1.5,0.5,0.5,unit = "line"),
        legend.text = element_text(size = 12, color = "black"),
        legend.title = element_text(size = 14, color = "black"),
        strip.text = element_text(colour = "black", size = 12, hjust = 0),
        strip.background = element_rect(colour="white", fill="white"),
        panel.border = element_rect(colour = NA, fill=NA),
        panel.spacing = unit(0.5, "cm"), aspect.ratio=0.5)
plot_coefficients_by_location_diff

filename = file.path(plot_path, "Nat_avert_continuous_timing_coefficient_matrix_diff.jpg")
ggsave(filename, plot_coefficients_by_location_diff, width = 12, height = 10)

## percentage with positive slope
test_diff <- states_regression_diff %>% 
  filter(location != "US") %>%
  filter(!is.na(coeff)) %>%
  mutate(slope_sign = if_else(coeff > 0, 1, 0),
         index = 1) %>%
  #group_by(scenario) %>%
  mutate(total = sum(index),
         pos = sum(slope_sign),
         perc_pos = 100*pos/total
  ) #%>%
#select(perc_pos, scenario) %>% distinct()

```


## Check Ensemble MHW spread
```{r}

ensemble_path <- paste(repo_path, folder_path, "2025-04-27/Ensemble/inc hosp/US/Ensemble0.gz.parquet", sep = "")

## grab MHW
  dt_ensemble_median_horizon <- arrow::open_dataset(ensemble_path) %>% 
    as.data.frame() %>%
    filter(age_group == "0-130") %>%
      group_by(scenario_id, output_type_id) %>%
      arrange(horizon, .by_group = TRUE) %>%  # Ensure values are in horizon order
      mutate(
        cum_value = cumsum(value),
        total_value = sum(value),
        prop_cum = cum_value / total_value
      ) %>%
      filter(prop_cum >= 0.5) %>%
      slice_min(prop_cum, with_ties = FALSE) %>%
      select(scenario_id, output_type_id,median_horizon = horizon, cumulative_value = cum_value)
  
  # convert horizon week to MMWR epi week
  dt_ensemble_median_horizon$ew = proj_MMWR$MMWRweek[dt_ensemble_median_horizon$median_horizon]


# find proportion of cumulative at horizon==26, scenario A
df_prop_cum_a <- arrow::open_dataset(ensemble_path) %>% 
    as.data.frame() %>%
    filter(age_group == "0-130") %>%
  group_by(scenario_id, output_type_id) %>%
  arrange(horizon, .by_group = TRUE) %>%  # Ensure values are in horizon order
  mutate(
    cum_value = cumsum(value),
    total_value = sum(value),
    prop_cum = cum_value / total_value
  ) %>%
  mutate(half_week = if_else(
    prop_cum >= 0.5, "Post", "Pre")
    ) %>%
  ## want the minimum week in the Post group 
  group_by(scenario_id, output_type_id, half_week) %>%
  ## group by half_week and if we are in the half_week == Post group, then set it to minimum horizon of that group
  ## If we are in the Pre group, set it to -1
  mutate(half_week2 = if_else(half_week == "Post", min(horizon), -1)) %>%
  ungroup() %>%
  group_by(output_type_id) %>%
  ## then grab the max across both pre/post, which will return min of post
  mutate(median_horizon = max(half_week2)) %>%
  filter(horizon == 26) %>%
  select(scenario_id, output_type_id, prop_cum=prop_cum, median_horizon, tot=total_value)


```



## View vaccine coverage curves - national
```{r}

dates <- read_csv("../SMH Round 19/data/auxiliary/COVID_RD19_Vaccination_curves.csv") %>%
  filter(Geography == "National", Scenario == "Scenarios B & D", Risk_group == "Overall") %>%
  dplyr::select(Date) %>% distinct() %>%
  mutate(MMWRweek(Date)) %>%
  arrange(Date)

vax_sat <- read_csv("../SMH Round 19/data/auxiliary/COVID_RD19_Vaccination_curves.csv") %>%
  filter(Geography == "National", Scenario == "Scenarios B & D", Risk_group == "Overall") %>%
  group_by(Age) %>%
  filter(`Cum.Coverage.Percent` >= 0.5*max(`Cum.Coverage.Percent`)) %>%
  ungroup() %>%
  ggplot(aes(x = Date, y = Cum.Coverage.Percent, color = Age)) + 
  geom_line() + 
  scale_x_continuous(breaks = dates$Date,labels = dates$MMWRweek)
vax_sat
```



## Regression table -- Figure 5 I

```{r}

get_regression_coefficients_5I <- read_csv("data/df_averted_long.csv") %>% 
                             filter(location == "US") %>%
                             mutate(scenario = paste("Scenario ", scenario, sep = ""))

list_regressions <- get_regression_coefficients_5I %>% 
  dplyr::select(model_id, scenario) %>% distinct()

coeffs_table <- NULL

for (i in 1:nrow(list_regressions)){
  regression_model_out <- lm(rel_vec_perc ~ median_horizon, data = get_regression_coefficients_5I %>% filter(model_id == list_regressions$model_id[i], scenario == list_regressions$scenario[i]))
  out_df_coeff <- coef(summary(regression_model_out)) %>%
    as.data.frame()
out_df_coeff  <- tibble::rownames_to_column(out_df_coeff, "Term") %>%
  mutate(Term = if_else(Term == "median_horizon", "Slope", "Intercept")) %>%
  mutate(`[0.025` = confint(regression_model_out)[,1],
         `0.975` = confint(regression_model_out)[,2]
         ) %>%
    mutate_if(is.numeric, round, digits=3) %>%
  mutate(model_id = list_regressions$model_id[i], scenario = list_regressions$scenario[i])

coeffs_table <- coeffs_table %>% rbind(out_df_coeff)
}

coeffs_tableB <- coeffs_table %>% filter(scenario == "Scenario B") %>% 
  arrange(model_id) %>%
  dplyr::select(-scenario)
coeffs_tableC <- coeffs_table %>% filter(scenario == "Scenario C") %>% 
  arrange(model_id) %>%
  dplyr::select(-scenario)
coeffs_tableD <- coeffs_table %>% filter(scenario == "Scenario D") %>% 
  arrange(model_id) %>%
  dplyr::select(-scenario)
coeffs_tableE <- coeffs_table %>% filter(scenario == "Scenario E") %>% 
  arrange(model_id) %>%
  dplyr::select(-scenario)

write_csv(coeffs_tableB, "data/coeffs_tableB.csv")
write_csv(coeffs_tableC, "data/coeffs_tableC.csv")
write_csv(coeffs_tableD, "data/coeffs_tableD.csv")
write_csv(coeffs_tableE, "data/coeffs_tableE.csv")

```

## Regression table -- Figure 5 II

```{r}

get_regression_coefficients_5II <- read_csv("data/df_averted_diff_long.csv") %>% 
                             filter(location == "US") %>%
                             mutate(scenario = paste("Scenario ", scenario, sep = ""))

list_regressions <- get_regression_coefficients_5II %>% 
  dplyr::select(model_id, scenario) %>% distinct()

coeffs_table <- NULL

for (i in 1:nrow(list_regressions)){
  regression_model_out <- lm(rel_vec_perc ~ median_horizon, data = get_regression_coefficients_5II %>% filter(model_id == list_regressions$model_id[i], scenario == list_regressions$scenario[i]))
  out_df_coeff <- coef(summary(regression_model_out)) %>%
    as.data.frame()
out_df_coeff  <- tibble::rownames_to_column(out_df_coeff, "Term") %>%
  mutate(`[0.025` = confint(regression_model_out)[,1],
         `0.975` = confint(regression_model_out)[,2]
         ) %>%
    mutate_if(is.numeric, round, digits=3) %>%
  mutate(Term = if_else(Term == "median_horizon", "Slope", "Intercept")) %>%
  mutate(model_id = list_regressions$model_id[i], scenario = list_regressions$scenario[i])

coeffs_table <- coeffs_table %>% rbind(out_df_coeff)
}


coeffs_tableBC <- coeffs_table %>% filter(scenario == "Scenario diff_BC") %>% 
  arrange(model_id) %>%
  dplyr::select(-scenario)
coeffs_tableDE <- coeffs_table %>% filter(scenario == "Scenario diff_DE") %>% 
  arrange(model_id) %>%
  dplyr::select(-scenario)


write_csv(coeffs_tableBC, "data/coeffs_table_BCdiff.csv")
write_csv(coeffs_tableDE, "data/coeffs_table_DEdiff.csv")

```






